---
title: "W_UP_01"
author: "Sandra Iovino"
date: "Summer 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups that line can do in 2 minutes, compared to skill

$H_A$: The average number of pushups done by 2 minutes line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
 Pushups is a numerical number   
 Skill is categorical variable  
 we predict push ups based on positions, viz ( mainly)  
 Pushups~position  
 we use helper file  
NUM~CAT 

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

 This box plot shows that skills position do more pushups in 2 minutes than line players.    

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```
 This shows that the skill player can do an average of 50 pushups in 2 minutes than the line players, that only do about 17 pushups in 2 minutes.   

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)

```
In the Ttest it shows that the P-Value is 9.421e-06. This will come out to have the Pvalue is .000009. The pvalue is less than 0.05 so we reject the null hypothesis and conclude there is a difference when line player do pushes and skilled players.  


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
Our job was to see if line players can do more pushups than skilled players under 2 minutes. When graphing results it shows that skilled players can do more pushups than Line players under 2 minutes. When doing the numerical results it shows that skilled players can do about 50 push ups under 2 mins and Line players can do roughly 17 pushups under 2 minutes. When doing the T test it shows that we reject the null hypothesis since Pvalue was less than 0.05. This means that there is a difference when skilled players do pushups in 2 minutes.  
